Depression and suicidality as costly signals of need

### 2021-03-18 Paper.rmd
Commit to pull Michael's changes

```{r setup, include=F}
knitr::opts_chunk$set(echo = F, warning = F, error = F, message = F)
source('analysis.R')
library(equatiomatic)
```

@@

`r extract_eq(m1, intercept = 'beta', wrap = T)`

@@

>>>>

```{r setup, include=F}
knitr::opts_chunk$set(echo = F, warning = F, error = F, message = F)
# source('analysis.R')
tar_load(c('models', 'effectsPlots', 'plot_T1Belief_T1Action'))
library(equatiomatic)
```

@@

@@

```{r t1plot}
plot_T1Belief_T1Action
```
